---
title: "Clean Raw Data"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

librarian::shelf("freeR", "glue", "googledrive", "here", "janitor", "lubridate", "readxl", "tidyverse")

options(scipen=999)

dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/Palmyra_DataTransfer_EDI_Project"
```

## Read in the Data from Google Drive 

To do this step, you need to have Google Drive installed on your computer so that you can access Google Drive files using Google File Stream 

```{r}

# you can use read_csv, readxl, etc to read in files here as if you were doing it from your local machine. 
# Example below 
# chlorurus_activity <- read_csv(glue("{dir_gdrive}/DATA_RAW/Peter Carlson/Chlorurus_Activity_data.csv")) %>% 
#   clean_names()

# To add multiple files from the drive into a tibble 
# multiple_files <- tibble(list.files(glue("{dir_gdrive}/DATA_RAW/Peter Carlson/"), pattern = ".csv"))



```


## Explore the Data 

```{r}



```


### Highlight Changes Required 

You can add a bullet point list here 




## Clean the Data 

```{r}



```

## Save the Clean Data 

Use this code chunk to upload the cleaned data directly to google drive. You write the file directly to the drive as if you were saving it to a local file 

```{r}
# You can use write_csv or any other function like that to write directly to the drive. 

# Example below: 
# write_csv(chlorurus_activity, glue("{dir_gdrive}/DATA_RAW/Peter 
# Carlson/Chlorurus_Activity_Palmyra_2014-test.csv"))



```



