---
title: "ADD TILE"
author: "ADD AUTHOR"
date: "ADD DATE"
output: word_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(EMLassemblyline)
library(flextable)

```

Please **revise and fill in** as much information as possible. Fields highlighted in yellow must be completed.


The information in this document will be used to create the EML of the data package to be published on the [Environmental Data Initiative (EDI) repository](https://portal.edirepository.org/nis/home.jsp).

## 1. Data Package Title




## 2. Dataset Title
<!--_Include what, where, and when in the dataset title_-->
 - 
 - 
 

## 3. Abstract
_Please provide an abstract specifically of the dataset. This is different from the abstract of an associated publication. Include what, why, where, when, and how_

[See example here](https://docs.google.com/document/d/1KdHJObHl5Bxxr9t0LISTwX0cCSVvx7NPUjz5T_P9JEc/edit#)

 


## 4. Creators
_These are the people who will show up as authors in the dataset citation. These are the individuals who have provided intellectual or other significant contributions to the creation of this dataset. **Please add a row with the information of each individual that should be part of the authorship of this dataset.**_

**We highly encourage you to create an ORCID if you don't already have one.** [Find more information here.](https://info.orcid.org/what-is-orcid/)

```{r, creator table, echo = FALSE, message= FALSE, warning= FALSE}

first_name <- c("", "")
middle_in <- c("", "")
last_name <- c(" ", " ")
organization <- c("", "")
email <- c("", "")
orcid <- c("", "")

creator_colname <- c("First Name", "Middle Initial", "Last Name", "Organization", "email address", "ORCID ID")

creator_table <- tibble(first_name, middle_in, last_name, organization, email, orcid)

colnames(creator_table) <- creator_colname

```


```{r, creators table export, echo=FALSE, message= FALSE, warning= FALSE, results = 'asis'}

set_flextable_defaults(big.mark = " ", 
  font.size = 10, 
  theme_fun = theme_box)


flextable::flextable(creator_table) %>% 
  width(width = 1)
  #autofit(add_w = 0.1, add_h = 0.1, part = c("body", "header"), unit = "in")
```


## 5. Other personnel names and roles 

_Who should a data user contact with questions about this data?_
_There must be at least one person or organization name to serve as the contact for this dataset._
_You may also list other personnel who participated in the project (such as field crew, lab tech, data entry, etc.) in this table with optional fields, email addresses, organization, and ORCID ID._


**We highly encourage you to create an ORCID if you don't already have one.** [Find more information here.](https://info.orcid.org/what-is-orcid/)


```{r, personnel table, echo = FALSE, message= FALSE, warning= FALSE}

p_first_name <- c("", "Camila")
p_middle_in <- c("", "")
p_last_name <- c(" ", "Vargas Poulsen")
p_organization <- c(" ", "PADL Data Manager, University of California Santa Barbara")
p_email <- c("", "camilavargas@ucsb.edu")
p_orcid <- c("", "")
p_role <- c("contact", "associated party")

personnel_colnames <- c("First Name", "Middle Initial", "Last Name", "Organization", "email address", "ORCID ID", "Role in project")


personnel_table <- tibble(p_first_name, p_middle_in, p_last_name, p_organization, p_email, p_orcid, p_role)

colnames(personnel_table) <- personnel_colnames

```


```{r, personnel table export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(personnel_table) %>% 
  width(width = 1)
```


## 6. License 
_**Please highlight** the license for the release of your data. Click on the license name for more information._ 

[CCO](https://creativecommons.org/publicdomain/zero/1.0/)


Public Domain Dedication, aka “No Rights Reserved.” This one means, “If I hold copyright in this, I waive it."


Consultation with the original investigators is strongly encouraged but not necessary. Publications and data products that make use of the dataset should include proper acknowledgement.

or

[CC BY](https://creativecommons.org/licenses/by/4.0/)

Attribution is required. CC licenses require that those who reuse a work provide attribution to the work’s creator by retaining “identification of the creator(s) of the Licensed Material and any others designated to receive attribution, in any reasonable manner requested by the Licensor (including by pseudonym if designated).”

**Message for user:** Data user is required to cite it appropriately in any publication that results from its use. 

## 7. Keywords
_Using keywords from a controlled vocabulary (CV) will improve your data's future discovery and reuse.  The LTER CV is a good source for keywords. Access the [LTER CV here](https://vocab.lternet.edu/vocab/vocab/index.php).  Also, please determine one or two keywords that best describe your lab, station, and/or project (e.g., Trout Lake Station, NTL LTER).). Add as many rows to this table as needed_

- Palmyra Atoll




## 8. Funding of this work
_List only the main PI of a grant that supported this project, starting with the main grant first.  Add rows to the table if several grants were involved._


```{r, funding table, echo = FALSE, message= FALSE, warning= FALSE, message= FALSE, warning= FALSE}

pi_first_name <- " "
pi_middle_in <- " "
pi_last_name <- " "
pi_email <- " "
pi_orcid <- " "
title_grant <- " "
fund_agency <- " "
fund_id <- " "

fund_colnames <- c("PI First Name", "PI Middle Initial", "PI Last Name", "PI email", "PI ORCID ID", "Title of Grant", "Funding Agency", "Funding Identification Number")


funding_table <- tibble(pi_first_name, pi_middle_in, pi_last_name, pi_email, pi_orcid, title_grant, fund_agency, fund_id)

colnames(funding_table) <- fund_colnames

```


```{r, funding table export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(funding_table) %>% 
  width(width = 1)
  
```



## 9. Timeframe

```{r, timefram table, echo = FALSE, message= FALSE, warning= FALSE}

Information <- c("Begin date", "End date", "Is data collection ongoing or completed?")

Description <- c(" ", "", "Completed")

timeframe_table <- tibble(Information, Description)

flextable::flextable(timeframe_table) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")

```



## 10. Geographic location

_Use decimal degrees to define a point or a bounding box._
Every point you add will be displayed on a map once the data package is published. [See example here](https://portal.edirepository.org/nis/mapbrowse?scope=knb-lter-sbc&identifier=108)

**Verbal description:** Palmyra Atoll

```{r, geographic location table, echo = FALSE, message= FALSE, warning= FALSE}

Directions <- c("Northbound", "Southbound", "Eastbound", "Westbound")

Coordinate <- c(5.88333, 5.871, -162.043, -162.083)

geo_loc_table <- tibble(Directions, Coordinate)

flextable(geo_loc_table) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")

```

**Copy this block to add multiple points or areas.**_

**Verbal description:**


```{r, geographic location table 2, echo = FALSE, message= FALSE, warning= FALSE}

coordinate <- c(" ", " ", " ", " ")

geo_loc_table_2 <- tibble(Directions, coordinate)

flextable(geo_loc_table_2) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")

```

## 11. Methods
_Be specific about the study design and field and lab methods for collecting and processing the data. Include instrument descriptions and protocol citations._

Find an example [in this link](https://docs.google.com/document/d/1KdHJObHl5Bxxr9t0LISTwX0cCSVvx7NPUjz5T_P9JEc/edit#)



## 12. Data Provenance

_Is this data derived from other data? If so, you will want to document this information, so users know where this data came from.  Please specify the source datasets used in the below provenance table, preferably with their DOI or URL.  [Here is an example of a dataset derived from several others](https://portal.edirepository.org/nis/mapbrowse?packageid=edi.101.3)._



```{r, data provenance, echo = FALSE, message= FALSE, warning= FALSE}

data_title <- c(" ", " ")
data_doi_url <- c("", "")
creator_name <- c("", "")
contact_email <- c("", "")

provenance_colnames <- c("Dataset title", "Dataset DOI or URL", "Creator Name", "Contact Email")


provenance_table <- tibble(data_title, data_doi_url, creator_name, contact_email)

colnames(provenance_table) <- provenance_colnames

```


```{r, provence table, export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(provenance_table) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
```



## 13. Data Table

Each row in the below table describes one column in your data table.  Complete each row as follows:

- **Description:** Please give a specific definition of the column name. This can be lengthy.
- **Unit:** Identify units for all numeric variables. All rows where there is an * under the unit column must be filled in with a unit.
- **Date format:** Please tell us exactly how the date and time are formatted: e.g., mm/dd/yyyy hh:mm:ss, plus the time zone and whether daylight savings were observed.  ISO date format of YYYY-MM-DD or YYYY-MM-DD hh:mm:ss is preferred.
- **Missing value code:** If a code for ‘no data’ is used, please specify: e.g., -99999, NA
- **Missing value code Explanation:** Why are these values missing? e.g.: value not available, value not recorded.


**Table name:** (Add a short name for this table)
**Table description:** (Add brief description of table contents)


```{r, create data attributes tables, echo = FALSE, message= FALSE, warning= FALSE}

## Location of datasets in the package

path_data <- here::here("7.clean_data")
path_templates <- here::here("3.data_attributes")

#-----------------------------------------------------------------#


## If there is just one file in 7.clean_data run this code
## **UPDATE NAMES**

# file1_name <- "FILE NAME"
# 
# ## Creating the attribute .txt
# EMLassemblyline::template_table_attributes(
#   path = path_templates,
#   data.path = path_data,
#   data.table = paste0(file1_name, ".csv"))
# 
# ## reading text into a data frame
# data_attributes1 <- read.delim2(here::here(paste0("3.data_attributes/attributes_", file1_name, ".txt"))) %>% 
#   mutate(unit = case_when(unit == "!Add units here!" ~ "*"))

#------------------------------------------------------------------#

## If there is more than one data set in 7.clean_data, run this code

## Create table with all the file names
files_names <- tibble(
  list.files(path_data, pattern = "csv")) %>% 
  rename(file_name = 1) %>% 
  mutate(file_name = str_remove(file_name, ".csv"),
         attribute_name = paste0("data_attributes", 1:n()),
         position = 1:n())

## Creating the attribute .txt

for (i in files_names$file_name){

  EMLassemblyline::template_table_attributes(
  path = path_templates,
  data.path = path_data,
  data.table = paste0(i, ".csv"))
}

## reading text into a data frame

##General function
read_attribute <- function(test){
  
  read.delim2(here::here(paste0("3.data_attributes/attributes_", test, ".txt"))) %>% 
  mutate(unit = case_when(unit == "!Add units here!" ~ "*"))
}

## Loop to read and name each file 
for (i in files_names$position){
  
  assign(files_names$attribute_name[i], read_attribute(files_names$file_name[i]))

  }


```



```{r, attribute table 1, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(data_attributes1) %>% 
  width(width = 1)

```


```{r, attribute table 2, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(data_attributes2) %>% 
  width(width = 1)

```

## 14. Attributes code

_If you use codes in your column, please define each code in the following table. **Fill in only if necessary**_ 



```{r, attribute code, echo = FALSE, message= FALSE, warning= FALSE}

## Note: there can only be one file with he prefix attribute_ in the data attribute folder.
EMLassemblyline::template_categorical_variables(
  path = path_templates,
  data.path = path_data)

# **UPDATE NAMES**

cat_vars <- read.delim2(here::here(paste0("3.data_attributes/catvars_", file1_name,".txt")))

```


```{r, categorical variables table, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(cat_vars) %>%
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
  

```



<!-- ### Spatial data objects

(List any geospatial data objects you would like to archive. Organize spatial data into .zip directories
and describe each.)
Directory name: (A short name for the data)
Directory description: (A brief description of the data)

Horizontal Coordinate System Name (e.g. WGS_1984_UTM_Zone_12N)
Horizontal Accuracy Report
Vertical Accuracy Report
Cell Size X Direction
Cell Size Y Direction
Raster Origin (e.g. Upper Left)
Number of Rows
Number of Columns
Number of Verticals
Cell Geometry (e.g. pixel) -->


## 15. Scripts/code (software)

_List any software scripts/code you would like to archive along with your data. These may include processing scripts you wrote to create, clean, or analyze the data._


```{r, script info, echo = FALSE, message= FALSE, warning= FALSE}

file_name <- " "
description <- " "
language <- " "


script_info_colnames <- c("Filename", "Description", "Scripting language")


script_info <- tibble(file_name, description, language)

colnames(script_info) <- script_info_colnames

```


```{r, script info export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(script_info) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
```




## 16. Other objects (misc.)
_List any other objects (e.g., .zip, .pdf, etc.) you would like to archive._

**Note:** At the moment, we are not including any photographic data.


```{r, other objects, echo = FALSE, message= FALSE, warning= FALSE}

misc_file_name <- " "
misc_description <- " "
misc_data_type <- " "


other_obj_colnames <- c("Filename", "Description", "Data type")

other_objects <- tibble(misc_file_name, misc_description, misc_data_type)

colnames(other_objects) <- other_obj_colnames

```


```{r, other objects export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(other_objects) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
```


## 17. Articles
_List articles citing this dataset. Add as many rows as necessary_


```{r, publications, echo = FALSE, message= FALSE, warning= FALSE}

doi <- " "
article_title <- " "
journal <- " "


publications_colnames <- c("Article DOI or URL (DOI is preferred)", "Article title", "Journal title")

publications <- tibble(doi, article_title, journal)

colnames(publications) <- publications_colnames

```


```{r, publications export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(publications) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
```


## Notes, Comments, and Questions
_Please let us know if you have any additional comments or questions about your data or the EML information. THANK YOU!_







